The development of infants' responses to mispronunciations: A Meta-Analysis

### 2019-06-03 VonHolzenBergmann_MPMetaAnalysis.tex
first draft of monster paper, updated random effects structure

In designing their mispronunciation stimuli, Swingley and Aslin (2000)
chose consonant mispronunciations that were likely to confuse adults
(Miller \& Nicely, 1955). Subsequent research has settled on
systematically modulating phonemic features to achieve mispronunciations
of familiar words. By utilizing mispronunciations consisting of phonemic
changes, these experiments examine infants' sensitivity to factors that
change the identity of a word on a measurable level (i.e.~1-feature,
2-features, 3-features, etc.). The importance of controlling for the
degree of phonological mismatch, as measured by number of features
changed, is further highlighted by studies that find graded sensitivity
to both consonant (White \& Morgan, 2008) and vowel (Mani \& Plunkett,
2011) feature changes. The greater the number of features changed, or
\emph{mispronunciation size}, the easier it may be to detect a
mispronunciation, whereas more similar mispronunciations may be more
difficult to detect.

@@

We first generated a list of potentially relevant items to be included
in our meta-analysis by creating an expert list. This process yielded
110 items. We then used the google scholar search engine to search for
papers citing the original Swingley and Aslin (2000) publication. This
search was conducted on 22 September, 2017 and yielded 288 results. We
removed 99 duplicate items and screened the remaining 299 items for
their title and abstract to determine whether each met the following
inclusion criteria: (1) original data was reported; (2) the experiment
examined familiar word recognition and mispronunciations; (3) infants
studied were under 31-months-of-age and typically developing; (4) the
dependent variable was derived from proportion of looks to a target
image versus a distractor in a eye movement experiment; (5) the stimuli
were auditory speech. The final sample (n = \emph{32}) consisted of 27
journal articles, 1 proceedings paper, 2 theses, and 2 unpublished
reports. We will refer to these items collectively as papers. Table 1
provides an overview of all papers included in the present
meta-analysis.

@@

A detailed explanation for moderating factors 3-8 can be found in their
respective sections in the Results. We separated conditions according to
whether or not the target word was mispronounced to be able to
investigate infants' looking to the target picture as well as their
mispronunciation sensitivity, which is the difference between looks to
the target in correct and mispronounced trials. When the same infants
were further exposed to multiple mispronunciation conditions and the
results were reported separately in the paper, we also entered each
condition as a separate row (e.g., consonant versus vowel
mispronunciations; Mani \& Plunkett, 2007). The fact that the same
infants contributed data to multiple rows (minimally those containing
information on correct and mispronounced trials) leads to shared
variance across effect sizes, which we account for in our analyses (see
next section). We will call each row a record; in total there were 251
records in our data.

@@

We first calculated the meta-analytic effect for infants' ability to
identify objects when hearing correctly pronounced labels. The
variance-weighted meta-analytic effect size Hedges' \emph{g} was 0.908
(SE = 0.12) which was significantly different from zero (CI {[}0.673,
1.143{]}, \emph{p} \textless{} .001). This is a small to medium effect
size (according to the criteria set by Mills-Smith, Spangler, Panneton,
\& Fritz, 2015). That the effect size is significantly above zero
suggests that when presented with the correctly pronounced label,
infants tended to fixate on the corresponding object. Although the
publication bias present in our analysis of funnel plot asymmetry
suggests that the effect size Hedges' \emph{g} may be overestimated for
object identification in response to correctly pronounced words, the
p-curve results and a CI lower bound of 0.67, which is substantially
above zero, together suggest that this result is somewhat robust. In
other words, we are confident that the true population mean lies above
zero for object recognition of correctly pronounced words.

We then calculated the meta-analytic effect for object identification in
response to mispronounced words. In this case, the variance-weighted
meta-analytic effect size Hedges' \emph{g} was 0.25 (SE = 0.06) which
was also significantly different from zero (CI {[}0.133, 0.367{]},
\emph{p} \textless{} .001). This is considered a small effect size
(Mills-Smith et al., 2015), but significantly above zero, which suggests
that even when presented with a mispronounced label, infants fixated the
correct object. In other words, infants are able to resolve
mispronunciations, a key skill in language processing We again note the
publication bias (which was smaller in this condition), and the
possibility that the effect size Hedges' \emph{g} may be overestimated.
But, as the p-curve indicated evidential value, we are confident in the
overall pattern, namely that infants fixate the target even after
hearing a mispronounced label.

@@

The above two analyses considered the data from mispronounced and
correctly pronounced words separately. To evaluate mispronunciation
sensitivity, we compared the effect size Hedges' \emph{g} for correct
pronunciations with mispronunciations directly. To this end, we combined
the two datasets. When condition was included (correct, mispronounced),
the moderator test was significant (QM(1) = 215.761, \emph{p}
\textless{} .001). The estimate for mispronunciation sensitivity was
0.495 (SE = 0.034), and infants' looking behavior across conditions was
significantly different (CI {[}0.429, 0.561{]}, \emph{p} \textless{}
.001). This confirms that although infants fixate the correct object for
both correct pronunciations and mispronunciations, the observed
fixations to target (as measured by the effect sizes) were significantly
greater for correct pronunciations. In other words, we observe a
significant difference between the two conditions and can now quantify
the modulation of fixation behavior in terms of standardized effect
sizes and their variance. This first result has both theoretical and
practical implications, as we can now reason about the amount of
perturbation caused by mispronunciations and can plan future studies to
further investigate this effect with suitable power.

@@

In the first analyses, we investigate the impact of age separately on
conditions where words were either pronounced correctly or not. Age did
not significantly modulate object identification in response to
correctly pronounced (QM(1) = 0.678, \emph{p} = 0.41) or mispronounced
words (QM(1) = 1.715, \emph{p} = 0.19). The lack of a significant
modulation together with the small estimates for age (correct: \(\beta\)
= 0.015, SE = 0.018, 95\% CI{[}-0.02, 0.049{]}, \emph{p} = 0.41;
mispronunciation: \(\beta\) = 0.015, SE = 0.011, 95\% CI{[}-0.007,
0.037{]}, \emph{p} = 0.19) indicates that there might be no relationship
between age and target looks in response to a correctly pronounced or
mispronounced label. We note that the estimates in both cases are
positive, however, which is in line with the general assumption that
infants' language processing overall improves as they mature (Fernald et
al., 1998). We plot both object recognition and mispronunciation
sensitivity as a function of age in Figure \ref{fig:PlotMPEffect}.

We then examined the interaction between age and mispronunciation
sensitivity (correct vs.~mispronounced words) in our whole dataset. The
moderator test was significant (QM(3) = 218.621, \emph{p} \textless{}
.001). The interaction between age and mispronunciation sensitivity,
however, was not significant (\(\beta\) = 0.003, SE = 0.008, 95\%
CI{[}-0.012, 0.018{]}, \emph{p} = 0.731); the moderator test was mainly
driven by the difference between conditions. The small estimate, as well
as inspection of Figure \ref{fig:PlotMPEffect}, suggests that as infants
age, their mispronunciation sensitivity neither increases or decreases.

@@

\subsubsection{Interim Discussion:
Meta-Analysis}\label{interim-discussion-meta-analysis}

@@

In this section, we consider each moderator individually and investigate
its influence on mispronunciation sensitivity. For most moderators
(except Number of features changed), we combine the correct and
mispronounced datasets and include the moderator of condition, to study
mispronunciation sensitivity as opposed to object recognition. To better
understand the impact of these moderators on developmental change, we
include age as subsequent moderator as well as an exploratory analysis
of the age of infants tested with each type of moderator. The latter
analysis is included to explore whether the lack of developmental change
in mispronunciation sensitivity in the overall dataset is due to more
complex moderator tasks being given to older infants, which may lower
the overall effect size of mispronunciation sensitivity at older ages
and dampen any evidence of change.

\subsubsection{Number of features
changed}\label{number-of-features-changed}

To assess whether the number of features changed modulates
mispronunciation sensitivity, we calculated the meta-analytic effect for
object identification in response to words that were pronounced
correctly and mispronounced using 1-, 2-, and 3-feature changes. We did
not include data for which the number of features changed in a
mispronunciation was not specified or the number of features changed was
not consistent (e.g., one mispronunciation included a 2-feature change
whereas another only a 1-feature change). This analysis was therefore
based on a subset of the overall dataset, with 81 experimental
conditions for correct pronunciations, 108 for 1-feature
mispronunciations, 16 for 2-feature mispronunciations, and 6 for
3-feature mispronunciations. Each feature change (from 0 to 3; 0
representing correct pronunciations) was considered to have an equal
impact on mispronunciation sensitivity, following the argument of graded
sensitivity (White \& Aslin, 2008; Mani \& Plunkett 2011), and this
modertor was coded as a continuous variable.

To understand the relationship between number of features changed and
mispronunciation sensitivity, we evaluated the effect size Hedges'
\emph{g} with number of features changed as a moderator. The moderator
test was significant, QM(1) = 137.214, \emph{p} \textless{} .001.
Hedges' \emph{g} for number of features changed was -0.306 (SE = 0.026),
which indicated that as the number of features changed increased, the
effect size Hedges' \emph{g} significantly decreased (CI {[}-0.357,
-0.255{]}, \emph{p} \textless{} .001). We plot this relationship in
Figure \ref{fig:PlotFeatEffect}. This confirms previous findings of a
graded sensitivity to the number of features changed for both consonant
(White \& Morgan, 2008) and vowel (Mani \& Plunkett, 2011)
mispronunciations as well as the importance of controlling for the
degree of phonological mismatch in experimental design.

\subsection{(Insert Figure \ref{fig:PlotFeatEffect} about
here)}\label{insert-figure-reffigplotfeateffect-about-here}

@@

Alternatively, an effect of maturation might have been masked by other
factors we have not yet captured in our analyses. A strong candidate
that emerged during the construction of the present dataset and careful
reading of the original papers was the analysis approach. We observed,
as mentioned in the Methods section, large variation in the dependent
variable reported, and additionally noted that the size of the chosen
post-naming analysis window varied substantially across papers.
Researchers might adapt their analysis strategy to infants' age or they
might be influenced by having observed the data. For example, consider
the possibility that there is a true increase in mispronunciation
sensitivity over development. In this scenario, younger infants should
show no or only little sensitivity to mispronunciations while older
infants would show a large sensitivity to mispronunciations. This lack
of or small mispronunciation sensitivity in younger infants is likely to
lead to non-significant results, which would be more difficult to
publish (C. J. Ferguson \& Heene, 2012). In order to have publishable
results, adjustments to the analysis approach could be made until a
significant, but spurious, effect of mispronunciation sensitivity is
found. This would lead to an increase in significant results and alter
the observed developmental trajectory of mispronunciation sensitivity.
Such a scenario is in line with the publication bias we observe
(Simmons, Nelson, \& Simonsohn, 2011). We examine whether variation in
the approach to data analysis may be have an influence on our
conclusions regarding infants' developing mispronunciation sensitivity.

>>>>

In designing their mispronunciation stimuli, Swingley and Aslin (2000)
chose consonant mispronunciations that were likely to confuse adults
(Miller \& Nicely, 1955). Subsequent research has settled on
systematically modulating phonemic features to achieve mispronunciations
of familiar words. By utilizing mispronunciations consisting of phonemic
changes, these experiments examine infants' sensitivity to factors that
change the identity of a word on a measurable level (i.e.~1-feature,
2-features, 3-features, etc.). The importance of controlling for the
degree of phonological mismatch, as measured by number of features
changed, is further highlighted by studies that find graded sensitivity
to both consonant (Bernier \& White, 2017; Tamasi, 2016; White \&
Morgan, 2008) and vowel (Mani \& Plunkett, 2011) feature changes. The
greater the number of features changed, or \emph{mispronunciation size},
the easier it may be to detect a mispronunciation, whereas more similar
mispronunciations may be more difficult to detect.

@@

We first generated a list of potentially relevant items to be included
in our meta-analysis by creating an expert list. This process yielded
110 items. We then used the google scholar search engine to search for
papers citing the original Swingley and Aslin (2000) publication. This
search was conducted on 22 September, 2017 and yielded 288 results. We
removed 99 duplicate items and screened the remaining 299 items for
their title and abstract to determine whether each met the following
inclusion criteria: (1) original data was reported; (2) the experiment
examined familiar word recognition and mispronunciations; (3) infants
studied were under 31-months-of-age and typically developing; (4) the
dependent variable was derived from proportion of looks to a target
image versus a distractor in a eye movement experiment; (5) the stimuli
were auditory speech. The final sample (\emph{n} = 32) consisted of 27
journal articles, 1 proceedings paper, 2 theses, and 2 unpublished
reports. We will refer to these items collectively as papers. Table 1
provides an overview of all papers included in the present
meta-analysis.

@@

A detailed explanation for moderating factors 3-8 can be found in their
respective sections in the Results.\footnote{Two papers tested bilingual
  infants (Ramon-Casas \& Bosch, 2010; Ramon-Casas et al., 2011),
  yielding 2 and 4 experimental conditions. Due to this small number, we
  do not investigate the role of multilingualism, but do note that
  removing these papers from the meta-analysis did not alter the pattern
  of results.} We separated conditions according to whether or not the
target word was mispronounced to be able to investigate infants' looking
to the target picture as well as their mispronunciation sensitivity,
which is the difference between looks to the target in correct and
mispronounced trials. When the same infants were further exposed to
multiple mispronunciation conditions and the results were reported
separately in the paper, we also entered each condition as a separate
row (e.g., consonant versus vowel mispronunciations; Mani \& Plunkett,
2007). The fact that the same infants contributed data to multiple rows
(minimally those containing information on correct and mispronounced
trials) leads to shared variance across effect sizes, which we account
for in our analyses (see next section). We will call each row a record;
in total there were 251 records in our data.

@@

We first calculated the meta-analytic effect for infants' ability to
identify objects when hearing correctly pronounced labels. The
variance-weighted meta-analytic effect size Hedges' \emph{g} was 0.916
(SE = 0.122) which was significantly different from zero (CI {[}0.676,
1.156{]}, \emph{p} \textless{} .001). This is a small to medium effect
size (according to the criteria set by Mills-Smith, Spangler, Panneton,
\& Fritz, 2015). That the effect size is significantly above zero
suggests that when presented with the correctly pronounced label,
infants tended to fixate on the corresponding object. Although the
publication bias present in our analysis of funnel plot asymmetry
suggests that the effect size Hedges' \emph{g} may be overestimated for
object identification in response to correctly pronounced words, the
p-curve results and a CI lower bound of 0.68, which is substantially
above zero, together suggest that this result is somewhat robust. In
other words, we are confident that the true population mean lies above
zero for object recognition of correctly pronounced words.

We then calculated the meta-analytic effect for object identification in
response to mispronounced words. In this case, the variance-weighted
meta-analytic effect size Hedges' \emph{g} was 0.249 (SE = 0.06) which
was also significantly different from zero (CI {[}0.132, 0.366{]},
\emph{p} \textless{} .001). This is considered a small effect size
(Mills-Smith et al., 2015), but significantly above zero, which suggests
that even when presented with a mispronounced label, infants fixated the
correct object. In other words, infants are able to resolve
mispronunciations, a key skill in language processing We again note the
publication bias (which was smaller in this condition), and the
possibility that the effect size Hedges' \emph{g} may be overestimated.
But, as the p-curve indicated evidential value, we are confident in the
overall pattern, namely that infants fixate the target even after
hearing a mispronounced label.

@@

The above two analyses considered the data from mispronounced and
correctly pronounced words separately. To evaluate mispronunciation
sensitivity, we compared the effect size Hedges' \emph{g} for correct
pronunciations with mispronunciations directly. To this end, we combined
the two datasets. When condition was included (correct, mispronounced),
the moderator test was significant (QM(1) = 103.408, \emph{p}
\textless{} .001). The estimate for mispronunciation sensitivity was
0.608 (SE = 0.06), and infants' looking behavior across conditions was
significantly different (CI {[}0.49, 0.725{]}, \emph{p} \textless{}
.001). This confirms that although infants fixate the correct object for
both correct pronunciations and mispronunciations, the observed
fixations to target (as measured by the effect sizes) were significantly
greater for correct pronunciations. In other words, we observe a
significant difference between the two conditions and can now quantify
the modulation of fixation behavior in terms of standardized effect
sizes and their variance. This first result has both theoretical and
practical implications, as we can now reason about the amount of
perturbation caused by mispronunciations and can plan future studies to
further investigate this effect with suitable power.

@@

In the first analyses, we investigate the impact of age separately on
conditions where words were either pronounced correctly or not. Age did
not significantly modulate object identification in response to
correctly pronounced (QM(1) = 0.558, \emph{p} = 0.455) or mispronounced
words (QM(1) = 1.64, \emph{p} = 0.2). The lack of a significant
modulation together with the small estimates for age (correct: \(\beta\)
= 0.014, SE = 0.019, 95\% CI{[}-0.022, 0.05{]}, \emph{p} = 0.455;
mispronunciation: \(\beta\) = 0.015, SE = 0.011, 95\% CI{[}-0.008,
0.037{]}, \emph{p} = 0.2) indicates that there might be no relationship
between age and target looks in response to a correctly pronounced or
mispronounced label. We note that the estimates in both cases are
positive, however, which is in line with the general assumption that
infants' language processing overall improves as they mature (Fernald et
al., 1998). We plot both object recognition and mispronunciation
sensitivity as a function of age in Figure \ref{fig:PlotMPEffect}.

We then examined the interaction between age and mispronunciation
sensitivity (correct vs.~mispronounced words) in our whole dataset. The
moderator test was significant (QM(3) = 106.158, \emph{p} \textless{}
.001). The interaction between age and mispronunciation sensitivity,
however, was not significant (\(\beta\) = 0.012, SE = 0.013, 95\%
CI{[}-0.014, 0.039{]}, \emph{p} = 0.349); the moderator test was mainly
driven by the difference between conditions. The small estimate, as well
as inspection of Figure \ref{fig:PlotMPEffect}, suggests that as infants
age, their mispronunciation sensitivity neither increases or decreases.

@@

\subsubsection{Interim discussion: Development of infants'
mispronunciation
sensitivity}\label{interim-discussion-development-of-infants-mispronunciation-sensitivity}

@@

In this section, we consider each moderator individually and investigate
its influence on mispronunciation sensitivity. For most moderators
(except Number of features changed), we combine the correct and
mispronounced datasets and include the moderator of condition, to study
mispronunciation sensitivity as opposed to object recognition. To better
understand the impact of these moderators on developmental change, we
include age as subsequent moderator as well as an exploratory analysis
of the age of infants tested with each type of moderator. The latter
analysis is included to explore whether the lack of developmental change
in mispronunciation sensitivity in the overall dataset is due to more
complex moderator tasks being given to older infants, which may lower
the overall effect size of mispronunciation sensitivity at older ages
and dampen any evidence of change. Finally, we analyze the relationship
between infant age and the moderator condition they were tested in using
Fischer's exact test, which is more appropriate for small sample sizes
(Fischer, 1922). For each moderator, we evaluate the independence of
infants' age group (divided into quartiles unless otherwise specified)
and assignment to each type of condition in a particular moderator.

\subsubsection{Size of mispronunciation}\label{size-of-mispronunciation}

To assess whether the size of the mispornunciation tested, as measured
by the number of features change, modulates mispronunciation
sensitivity, we calculated the meta-analytic effect for object
identification in response to words that were pronounced correctly and
mispronounced using 1-, 2-, and 3-feature changes. We did not include
data for which the number of features changed in a mispronunciation was
not specified or the number of features changed was not consistent
(e.g., one mispronunciation included a 2-feature change whereas another
only a 1-feature change). This analysis was therefore based on a subset
of the overall dataset, with 90 experimental conditions for correct
pronunciations, 99 for 1-feature mispronunciations, 16 for 2-feature
mispronunciations, and 6 for 3-feature mispronunciations. Each feature
change (from 0 to 3; 0 representing correct pronunciations) was
considered to have an equal impact on mispronunciation sensitivity,
following the argument of graded sensitivity (White \& Aslin, 2008; Mani
\& Plunkett 2011), and this modertor was coded as a continuous variable.

To understand the relationship between mispronunciation size and
mispronunciation sensitivity, we evaluated the effect size Hedges'
\emph{g} with number of features changed as a moderator. The moderator
test was significant, QM(1) = 61.081, \emph{p} \textless{} .001. Hedges'
\emph{g} for number of features changed was -0.406 (SE = 0.052), which
indicated that as the number of features changed increased, the effect
size Hedges' \emph{g} significantly decreased (CI {[}-0.507, -0.304{]},
\emph{p} \textless{} .001). We plot this relationship in Figure
\ref{fig:PlotFeatEffect}. This confirms previous findings of a graded
sensitivity to the number of features changed for both consonant
(Bernier \& White, 2017; Tamasi, 2016; White \& Morgan, 2008) and vowel
(Mani \& Plunkett, 2011) mispronunciations as well as the importance of
controlling for the degree of phonological mismatch in experimental
design.

To better understand how this moderator impacted our estimate of
developmental change in mispronunciation sensitivity, we added age as a
moderator. The moderator test was significant, QM(3) = 143.617, \emph{p}
\textless{} .001, but the interaction between age and number of features
changed was not significant, \(\beta\) = 0.009, SE = 0.006, 95\%
CI{[}-0.002, 0.02{]}, \emph{p} = 0.099. The small effect size for the
interaction between age and number of features changed suggests that the
impact of number of features changed on mispronunciation sensitivity
does not change with infant age. This may be due to the fact that only a
handful of studies have explicitly examined the effect of the number of
features changed on mispronunciation sensitivity and only these studies
include 3-feature changes (Bernier \& White, 2017; Tamasi, 2016; White
\& Morgan, 2008; Mani \& Plunkett, 2011).

The results of Fisher's exact test were not significant, \emph{p} =
0.703. This lack of a relationship suggests that older and younger
infants are not being tested in experimental conditions that
differentially manipulate the number of features changed.

@@

\subsubsection{Distractor familiarity}\label{distractor-familiarity}

To assess whether familiarity with the distractor image modulates
mispronunciation sensitivity, we calculated the meta-analytic effect for
object identification in response to words that were pronounced
correctly and mispronounced and were either paired with a familiar or
unfamiliar distractor. A familiar distractor was used in 179
experimental conditions and a unfamiliar distractor in 72 experimental
conditions.

To understand the relationship between distractor familiarity and
mispronunciation sensitivity, we evaluated the effect size Hedges'
\emph{g} with distractor familiarity and condition as moderators. The
moderator test was significant, QM(1) = 61.081, \emph{p} \textless{}
.001, but the effect of distractor familiarity (\(\beta\) = -0.12, SE =
0.144, 95\% CI{[}-0.403, 0.162{]}, \emph{p} = 0.403) as well as the
interaction between distractor familiarity and condition (\(\beta\) =
0.067, SE = 0.137, 95\% CI{[}-0.203, 0.336{]}, \emph{p} = 0.628) were
not significant. The results suggest that overall, infants' familiarity
with the distractor object (familiar or unfamiliar) did not impact their
mispronunciation sensitivity.

We next examined whether age modulates object recognition or
mispronunciation sensitivity when the distractor image is familiar or
unfamiliar. Based on previous results, we expected older infants to have
greater mispronunciation sensitivity than younger infants when the
distractor was unfamiliar compared to familiar. To evaluate this
prediction, we added age as a moderator. The moderator test was
significant QM(7) = 107.683, \emph{p} \textless{} .001. The estimate for
the three-way-interaction between condition, distractor familiarity, and
age was small and not significant (\(\beta\) = = NA, SE = NA, 95\%
CI{[}NA, NA{]}, \emph{p} NA. We note that in this model, the interaction
between condition and distractor familiarity was significant (\(\beta\)
= NA, SE = NA, 95\% CI{[}NA, NA{]}, \emph{p} NA, but that this estimate
is similar to the original, non-significant estimate specifically
examining this interaction in the previous model. Taken together, these
results suggest that regardless of age, mispronunciation sensitivity was
similar whether the distractor image was familiar or unfamiliar.

The results of Fisher's exact test were not significant, \emph{p} =
0.072. This lack of a relationship suggests that older and younger
infants are not being tested in experimental conditions that
differentially employ distractor images that are familiar or unfamiliar.

\subsubsection{Phonological overlap between target and
distractor}\label{phonological-overlap-between-target-and-distractor}

To assess whether phonological overlap between the target and distractor
image labels has an impact on the size of mispronunciation sensitivity,
we examined the meta-analytic effect for object identification in
response to mispronunciations and mispronunciation sensitivity when the
target-distractor pairs either had no overlap or shared the same onset
phoneme. We did not include data for which the overlap included both the
onset and medial phonemes (\emph{n} = 4), coda phonemes (\emph{n} = 3),
or for targets paired with an unfamiliar distractor image 60. The
analysis was therefore based on a subset of the overall dataset, with
104 experimental conditions containing onset phoneme overlap between the
target and distractor and 80 containing no overlap between target and
distractor.

To understand the relationship between phonological overlap between
target and distractor and mispronunciation sensitivity, we evaluated the
effect size Hedges' \emph{g} with distractor overlap and condition as
moderators. The moderator test was significant, QM(3) = 59.216, \emph{p}
\textless{} .001. The estimate for the interaction between condition and
distractor overlap was small, but significant (\(\beta\) = 0.275, SE =
0.157, 95\% CI{[}-0.033, 0.584{]}, \emph{p} = 0.08, suggesting that
mispronunciation sensitivity was greater when target-distractor pairs
shared the same onset phoneme compared to when they shared no
phonological overlap. This relationship be seen in Figure
\ref{fig:PlotDistOverlap}a.

To better understand how this moderator impacted our estimate of
developmental change in mispronunciation sensitivity, we added age as a
moderator. The moderator test was significant, QM(7) = 67.82, \emph{p}
\textless{} .001 and the estimate for the three-way interaction between
age, condition, and distractor overlap was significant, but relatively
small (\(\beta\) = = 0.091, SE = 0.038, 95\% CI{[}0.017, 0.166{]},
\emph{p} = 0.016. As can be seen in Figure \ref{fig:PlotDistOverlap}b,
mispronunciation sensitivity increases with age for target-distractor
pairs containing onset overlap, but decreases with age for
target-distractor pairs containing no overlap.

The results of Fisher's exact test were significant, \emph{p}
\textless{} .001. Older infants were more likely to be tested in
experimental conditions where target and distractor images overlapped on
their onset phoneme, while younger infants were more likely to be tested
with target and distractor images that did not control for overlap. A
distractor image that overlaps in the onset phoneme with the target
image is considered a more challenging task to the infant, as infants
must pay attention to the mispronounced phoneme and can not use the
differing onsets between target and distractor images to differentiate
(Fernald, Swingley, \& Pinto, 2001). It therefore appears that older
infants were given a more challenging task than younger infants. This
may explain why infants in the onset overlap condition, a harder task,
have a greater effect size estimate for mispronunciation sensitivity
than those in the no overlap condition, which is a comparably easier
task. We return to this issue in the General Discussion.

\begin{figure}
\centering
\includegraphics{VonHolzenBergmann_MPMetaAnalysis_files/figure-latex/PlotDistOverlap-1.pdf}
\caption{}
\end{figure}

\subsubsection{Position of
mispronunciation}\label{position-of-mispronunciation}

To assess whether the position of the mispronunciation has an impact on
mispronunciation sensitivity, we calculated the meta-analytic effect for
object identification in response to mispronunciations on the onset,
medial, and coda phonemes. We did not include data for which the
mispronunciation varied in regard to position (\emph{n} = 3, 29, 8, and
NA) or was not reported (\emph{n} = 10). The analysis was therefore
based on a subset of the overall dataset, with 143 and NA experimental
conditions comparing a mispronunciation on the onset phoneme, 48 and NA
experimental conditions comparing a mispronunciation on the medial
phoneme, and 10 and NA experimental conditions comparing a
mispronunciation on the coda phoneme. We coded the onset, medial, and
coda positions as continuous variables, to evaluate the importance of
each subsequent position (Marslen-Wilson \& Zwitserlood, 1989).

To understand the relationship between mispronunciation position and
mispronunciation sensitivity, we evaluated the effect size Hedges'
\emph{g} with mispronunciation position and condition as moderators. The
moderator test was significant, QM(3) = 172.345, \emph{p} \textless{}
.001. For the interaction between condition and mispronunciation
position, the estimate was small but significant (\(\beta\) = -0.126, SE
= 0.064, 95\% CI{[}-0.252, 0{]}, \emph{p} = 0.049. As can be seen in
Figure \ref{fig:PlotMispPosit}a, mispronunciation sensitivity decreased
linearly as the position of the mispronunciation moved later in the
word, with sensitivity greatest for onset mispronunciations and smallest
for coda mispronunciations.

To better understand how this moderator impacted our estimate of
developmental change in mispronunciation sensitivity, we added age as a
moderator. The moderator test was significant, QM(7) = 175.856, \emph{p}
\textless{} .001. The estimate for the three-way interaction between
age, condition, and mispronunciation position was not significant
(\(\beta\) = 0.022, SE = 0.018, 95\% CI{[}-0.013, 0.057{]}, \emph{p} =
0.223. As can be seen in Figure \ref{fig:PlotMispPosit}b,
mispronunciation sensitivity but stays relatively stable for onset and
medial mispronunciaitons. For mispronunciations on the coda position it
appears that mispronunciation sensitivity increases with age, but this
is likely underpowered and therefore not detectable by our
meta-analysis.

Due to the small sample size of coda mispronunciations, we only included
3 age groups in Fisher's exact test. The results were significant,
\emph{p} = 0.02. Older infants were more likely to be tested on onset
mispronunciations, while younger infants were more likely to be tested
on medial mispronunciations. An onset mispronunciation may be more
disruptive to lexical access than mispronunciations in subsequent
positions (Marslen-Wilson \& Zwitserlood, 1989), and therefore easier to
detect. For this reason, it is rather unsuprising that onset
mispronunciations show the greatest estimate of mispronunciation
sensitivity. However, it also means that younger infants, who were more
likely to be tested on medial mispronunciations, had a comparably harder
task than older infants, who were more likely to be tested on onset
mispronunciations. It is unlikely that this influenced our developmental
trajectory estimate, as the consequence would have been mispronunciation
sensitivity that increases with age.

\subsection{(Insert Figure 7 about
here)}\label{insert-figure-7-about-here}

\begin{figure}
\centering
\includegraphics{VonHolzenBergmann_MPMetaAnalysis_files/figure-latex/PlotMispPosit-1.pdf}
\caption{}
\end{figure}

\subsubsection{Type of mispronunciation (consonant or
vowel)}\label{type-of-mispronunciation-consonant-or-vowel}

To assess whether the type of mispronunciation impacts sensitivity to
mispronunciations, we calculated the meta-analytic effect for object
identification in response to the type of mispronunciation. Although
most theoretical discussion of mispronunciation type has focused on
consonants and vowels, our dataset also included tone mispronunciations.
In our analysis, we were interested in the difference between consonants
and vowels, but also include an exploratory analysis of responses to
tones, consonants, and vowels. Furthermore, sensitivity to consonant and
vowel mispronunciations is hypothesized to differ depending on whether
the infant is learning a Germanic or Romance language. We therefore
conducted two sets of analyses, one analyzing consonants and vowels
alone, a second including langauge family as a moderator, and a third
comparing responses to tones with that of consonants and vowels,
separately. For the latter analysis, tones were coded as the reference
condition. We did not include data for which mispronunciation type
varied within experiment and was not reported separately (\emph{n} = 21
and 2). The analysis was therefore based on a subset of the overall
dataset, with 145 experimental conditions comparing a consonant
mispronunciation, 71 experimental conditions comparing a vowel
mispronunciation, and 12 experimental conditions comparing a tone
mispronunciation. Below, we first report the set of analyses comparing
consonants with vowels and between language families before moving on to
the set of exploratory analyses comparing tones with that of consonants
and vowels.

To understand the relationship between mispronunciation type (consonant
or vowel) and mispronunciation sensitivity, we evaluated the effect size
Hedges' \emph{g} with mispronunciation type and condition as moderators.
The moderator test was significant, QM(7) = 153.795, \emph{p}
\textless{} .001, but the interaction between mispronunciation type and
condition (\(\beta\) = 0.056, SE = 0.079, 95\% CI{[}-0.099, 0.211{]},
\emph{p} = 0.479) was not significant. The results suggest that overall,
infants' sensitivity to consonant and vowel mispronunciations was
similar.

We next examined whether age modulates mispronunciation sensitivity when
the mispronunciation is a consonant or a vowel. When age was added as a
moderator, the moderator test was significant, QM(7) = 153.795, \emph{p}
\textless{} .001 and the estimate for the three-way interaction between
age, condition, and mispronunciation type was significant, but
relatively small (\(\beta\) = = 0.044, SE = 0.018, 95\% CI{[}0.008,
0.08{]}, \emph{p} = 0.016. As can be seen in Figure
\ref{fig:PlotMispType}b, as infants age, mispronunciation sensitivity
grows larger for vowel mispronunciations but stays steady for consonant
mispronunciations. Noticeably, mispronunciation sensitivity appears
greater for consonant compared to vowel mispronunciations at younger
ages, but this difference diminishes as infants age.

The results of Fisher's exact test were significant, \emph{p}
\textless{} .001. Older infants were more likely to be tested on
consonant mispronunciations, while younger infants were more likely to
be tested on vowel mispronunciations. It is not immediately clear
whether the relationship between infant age and type of mispronunciation
influences our estimate of how mispronunciation sensitivity changes with
development. Whether consonant or vowel mispronunciations are more
\enquote{difficult} is a matter of theoretical debate, but some evidence
suggest that it may be influenced by infants' native language (Nazzi,
Poltrock, \& Von Holzen, 2016). We next examined whether this was the
case.

\subsection{(Insert Figure 8 about
here)}\label{insert-figure-8-about-here}

\begin{figure}
\centering
\includegraphics{VonHolzenBergmann_MPMetaAnalysis_files/figure-latex/PlotMispType-1.pdf}
\caption{}
\end{figure}

To examine whether infants' native language impacts sensitivity to
consonant and vowel mispronunciations, we classified infants into
language families. Infants learning American English (\emph{n} = 56),
British English (\emph{n} = 66), Danish (\emph{n} = 6), Dutch (\emph{n}
= 58), and German (\emph{n} = 21) were classified into the Germanic
language family (\emph{n} = 207). Infants learning Catalan (\emph{n} =
4), Spanish (\emph{n} = 4), French (\emph{n} = 8), Catalan and Spanish
simultaneously (i.e.~bilinguals; \emph{n} = 6), and Swiss French
(\emph{n} = 6) were classified into the Romance language family
(\emph{n} = 28).

We assessed whether the relationship between mispronunciation type
(consonant or vowel) and mispronunciation sensitivity was modulated by
language family. We merged the two datasets and included condition
(correct pronunciation, mispronunciation) as well as language family as
additional moderators. The moderator test was significant, QM(7) =
158.889, \emph{p} \textless{} .001. The interaction between condition
and language family was significant (\(\beta\) = 0.727, SE = 0.231, 95\%
CI{[}0.274, 1.181{]}, \emph{p} = 0.002), suggesting that the estimate
for mispronunciation sensitivity was greater for infants learning a
Romance compared to Germanic language. However, when a model evaluating
this specific interaction, without mispronunciation type, was
calculated, the estimate was much smaller and not significant. This
suggests that the interaction between condition and language family may
be over-estimated. The three-way interaction between mispronunciation
type, condition, language family was large and also significant ,
\(\beta\) = -0.872, SE = 0.28, 95\% CI{[}-1.421, -0.323{]}, \emph{p} =
0.002. As can be seen in Figure @ref(fig:PlotCVEffect\_Lang)a,
mispronunciation sensitivity for consonants was similar for Germanic and
Romance languages. Mispronunciation sensitivity for vowels, however, was
greater for Germanic compared to Romance languages.
